### 2014-12-13 paper.tex
Remove section heading that was accidentally re-added
Expand conclusion a lttle

  We used a number of the metrics discussed in Section~\ref{background} to measure the compactness of districts.  To compute them, we used the geographic data from the U.S.~Census's TIGER/Line database~\cite{censustiger} on the shapes of congressional districts and census blocks, and where applicable, population data from the 2010~Census~\cite{census2010}.

@@

  \subsection{Relationship Between Compactness and Bias Measures}

@@

  \section{Conclusion}
  Partisan gerrymandering damages the fundamental nature of our representative democracy.  It produces unfair advantages that prevent citizens from being represented fairly.  Using quantifiable metrics of partisan gerrymandering, we hope to create a standard that can take out results that are blatantly biased, regardless of actual intent of those who created the plans.

  %TODO: more conclusioney stuff

>>>>

  We used a number of the metrics discussed in Section~\ref{s:background} to measure the compactness of districts.  To compute them, we used the geographic data from the U.S.~Census's TIGER/Line database~\cite{censustiger} on the shapes of congressional districts and census blocks, and where applicable, population data from the 2010~Census~\cite{census2010}.

@@

@@

  \section{Conclusion}
  Partisan gerrymandering damages the fundamental nature of our representative democracy.  It produces unfair advantages that prevent citizens from being represented fairly.  Real redistricting is too complex for a single simple metric to be able to quantify all types of gerrymandering, but by combining multiple metrics, it is possible to catch a number of different types of gerrymanders in a specific and quantifiable way.  Using quantifiable metrics of partisan gerrymandering, we hope to create a standard that can delineate results that are blatantly biased, regardless of any ability to discover the intent of those who created the plans.
